Estimating Neighborhood Rents with Scraped Data

### 2018-06-16 manuscript/index.Rmd
one more tweak to notation

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | `int`   | $\theta_{it} = \beta_0 + \gamma_t$
Non-Spatial              | `ns`    | $\theta_{it} = \beta_0 + \nu_i + \gamma_t$
Non-Spatial AR(1)        | `nsar1` | $\theta_{it} = \beta_0 + x_t + \phi_t + \nu_i$
BYM Spatial AR(1)        | `bym `  | $\theta_{it} = \beta_0 + x_t + \phi_t + v_i + \nu_i $
BYM Spatiotemporal AR(1) | `spt`   | $\theta_{it} = \beta_0 + x_t + \phi_t + v_i + \nu_i + \delta_{it}$

>>>>

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | `int`   | $\theta_{it} = \beta_0 + \gamma_t$
Non-Spatial              | `ns`    | $\theta_{it} = \beta_0 + \nu_i + \gamma_t$
Non-Spatial AR(1)        | `nsar1` | $\theta_{it} = \beta_0 + x_t + \phi_t + \nu_i$
BYM Spatial AR(1)        | `bym `  | $\theta_{it} = \beta_0 + x_t + \phi_t + v_i + \nu_i$
BYM Spatiotemporal AR(1) | `spt`   | $\theta_{it} = \beta_0 + x_t + \phi_t + v_i + \nu_i + \delta_{it}$
